--- 
title: 'Idaho Department of Fish and Game' 
author: 'PopR Population Model Report' 
output:
 html_document 
---
*** 


####Model Definition 
**Species:** *Mule Deer* 
**Unit:** *Boise River* 
**Years:** *1998*-*2015* 

####Future Harvest 

**Males:** *1210* 
**Females:** *968* 

####Demographic Settings 

**Adult Survival:** *Constant* 
**Juvenile Survival:** *Time Varying* 
**Recruitment:** *Time Varying* 

####Model Fitting 

**MCMC Burnin:** *10000* 
**MCMC Reps:** *18000* 
**Thinning Rate:** *1* 

***


####Population Size

 ```{r, echo = FALSE, results='asis'}

 source('C:/PopR_Master/custom/process_ipm.R')

 load('C:/PopR_Master/trash/tmp_model.RData') 

kable(mark_pop_tbl(out))

 ``` 

***




####Sex & Age Ratios

 ```{r, echo = FALSE, results='asis'}

 

kable(mark_rat_tbl(out))

 ``` 

***




####Survival

 ```{r, echo = FALSE, results='asis'}

 

kable(mark_surv_tbl(out))

 ``` 

***




####Population Trajectory

 ```{r, echo = FALSE, results='asis'}

 

mark_plot_N(summ_ipm(out), dat)

 ``` 

Figure 1. Model predicted population trajectory.  Solid line
represents the median estimate.  The shaded area depcits the 95%
prediction interval.  Blue dots represent the mean of field base 
estimates. 

***




####Population Growth Rate

 ```{r, echo = FALSE, results='asis'}

 

mark_plot_L(summ_ipm(out), dat)

 ``` 

Figure 1. Model predicted population growth rate.  The solid 
line represents the median estimate.  The shaded area depcits the 95% 
prediction interval. 

***

